A Fully Decentralized Infrastructure for Automated and Trusted IoT Data Trading

### 2020-05-31 paper.tex
Fix typo

\begin{abstract} 
The Internet of Things (IoT) makes our lives simple and easier by automating mundane processes with devices around us. Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy with other machines, which devices can share and trade their resources. For instance, smart meter data can assist in energy transition. Meanwhile, time smart meter data is privacy-sensitive, that implies power consumption can be associated with appliances used and eventually can be used to track somebody's behavior and location. Questions such as data ownership, data integrity and data privacy become new challenges in M2M economy. In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct an IoT-enabled, decentralized and trusted data marketplace on top of the IoT brokered infrastructure, in order to address the technical challenges. This approach can efficiently enhance the degree of transparency and scalability. The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers. Finally, we implement and elevuate the performance of the prototype.
\end{abstract}

@@

\subsection{Choice of Data Storage}
Data storage is an important element of data marketplace where the data assets are reserved. We assume such storage system should be distributed which runs on the peer-to-peer network maintiaining by multiple nodes. Hence, the risk of system paralysis for server being compromised or shutdown unexpectedly can be removed. Among the existing distributed storage mentioned in Section. CITE-RELATED-WORK, different architectures, back-up mechanisms and access controls strategies are proposed. Yet the keys and addresses of data managed by participants are hard to be as small as possible especially for data streams.

In our proposed architecture, MAM is the data storage which is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT. MAM allows users to put encrypted data streams into \textbf{channel}s and \textbf{endpoint}s, which consist of zero-value transactions on the Tangle. With an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data. Table.~\ref{tab:mam_scalability} compares the key and addresses that need to be managed by using MAM and other distributed storage systems. Assuming the length of data stream is 7, and each record is encrypted with the same key. With MAM, only 1 key and 1 entry point is required while other distributed storage need to reserve 7 entry points for each data record.

@@

>>>>

\begin{abstract} 
The Internet of Things (IoT) makes our lives simple and easier by automating mundane processes with devices around us. Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy with other machines, which devices can share and trade their resources. For instance, smart meter data can assist in energy transition. Meanwhile, time smart meter data is privacy-sensitive, that implies power consumption can be associated with appliances used and eventually can be used to track somebody's behavior and location. Questions such as data ownership, data integrity and data privacy become new challenges in M2M economy. In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct an IoT-enabled, decentralized and trusted data marketplace on top of the IoT brokered infrastructure, in order to address the technical challenges. This approach can efficiently enhance the degree of transparency and scalability. The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers. Finally, we implement and evaluate the performance of the prototype.
\end{abstract}

@@

\subsection{Choice of Data Storage}
Data storage is an important element of data marketplace where the data assets are reserved. We assume such storage system should be distributed which runs on the peer-to-peer network maintiaining by multiple nodes. Hence, the risk of system paralysis for server being compromised or shutdown unexpectedly can be removed. Among the existing distributed storage mentioned in Section~\ref{section:relatedWork}, different architectures, back-up mechanisms and access controls strategies are proposed. Yet the keys and addresses of data managed by participants are hard to be as small as possible especially for data streams.

%scalability
In our proposed architecture, MAM is the data storage which is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT. MAM allows users to put encrypted data streams into \textbf{channel}s and \textbf{endpoint}s, which consist of zero-value transactions on the Tangle. With an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data. Table.~\ref{tab:mam_scalability} compares the key and addresses that need to be managed by using MAM and other distributed storage systems. Assuming the length of data stream is 7, and each record is encrypted with the same key. With MAM, only 1 key and 1 entry point is required while other distributed storage need to reserve 7 entry points for each data record.

@@

%classify
With the channel and endpoint structures, users can easily categorized data streams with respect to different types and usages. For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs. Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statitics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products. To do the classification in other distributed storage also encounters the aforementioned scalability problem, data entrypoints of the data steams should be reserved.

%data trace
Moreover, data tracability is an important security issue that allows users to track the changes of data. Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity. Yet the hash values of each new version are unrelated and it's hard to point out the differences between versions. MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.
